Hypertension and microbiome

### 2019-01-01 rrbiome.Rmd
mclapply

```{r function for glm calculation, include = FALSE}
calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = "BL_AGE + SEX",
                            modelstring = "matrix ~ %s + %s",
                            npermutations = 99) {
    glmlist <- lapply(responses, function(response) {
        fo <- as.formula(sprintf(modelstring, response, covariates))
        ad <- adonis(fo, data = dset, permutations = npermutations)
        ad$aov.tab %>% as.data.frame
    }) 
}
```

>>>>

```{r function for adnoiscalculation, include = FALSE}
calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = "BL_AGE + SEX",
                            modelstring = "matrix ~ %s + %s",
                            npermutations = 99) {
    glmlist <- mclapply(responses, function(response) {
        fo <- as.formula(sprintf(modelstring, response, covariates))
        ad <- adonis(fo, data = dset, permutations = npermutations)
        ad$aov.tab %>% as.data.frame
    }, mc.cores = lenfth(responses)) 
}
```
